\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-03-25 journalSwarmControl/Introduction.tex
cleaned up intro

%Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion.  
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Limited computation and communication rules out autonomous operation or direct control over individual units; instead we must rely on global control signals broadcast to the entire particle population.  Additionally, many promising applications will require direct human control, but user interfaces to thousands---or millions---of particles is a daunting human-swarm interaction (HSI) challenge.  
This paper examines object manipulation by a swarm of particles, each actuated by the same, shared global input, as illustrated in Fig.~{\ref{fig:bigPictureMeanAndVarianceForSwarm}.

 This paper is the synthesis of two preliminary conference papers.  \cite{swarmcontrol2013} covered the first three months of SwarmControl.net experiments, and \cite{ShahrokhiIROS2015} presented simulations of object manipulation.  This paper presents three years of results from new games at SwarmControl.net.  For object manipulation, this paper presents robust new algorithms for manipulation, path planning, and obstacle avoidance, and a rich set of parametric studies.  All hardware validation experiments are new.

Our early work with over a hundred hardware robots and thousands of simulated particles demonstrated that direct human control of large swarms is possible, \cite{Becker2013b}. 
Unfortunately, the logistical challenges of repeated experiments with over one hundred robots prevented large-scale tests. 
There is currently no comprehensive understanding of user interfaces for controlling multi-robot systems with massive populations.  
This paper presents a tool for investigating HSI methods through statistically significant numbers of experiments.

\begin{figure}
\centering
%\begin{overpic}[height=6cm]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of particles, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the mean and variance of the robot distribution.  Here a swarm of particles pushes a green hexagon toward the goal 
%Simulation at left, screen capture from hardware experiment at right. 
(see also Extension 2).}
\end{figure}

>>>>

%Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion.  
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Limited computation and communication rules out autonomous operation or direct control over individual units; instead we must rely on global control signals broadcast to the entire particle population.    
This paper examines object manipulation by a swarm of particles, each actuated by the same, shared global input, as illustrated in Fig.~{\ref{fig:bigPictureMeanAndVarianceForSwarm}.

This paper combines the content of two preliminary conference papers, extending their substance and providing full details in a
single journal paper.
  \cite{swarmcontrol2013} covered the first three months of SwarmControl.net experiments, and \cite{ShahrokhiIROS2015} presented simulations of object manipulation.  This paper presents three years of results from new games at SwarmControl.net.  For object manipulation, this paper presents robust new algorithms for manipulation, path planning, and obstacle avoidance, and a rich set of parametric studies.  All hardware validation experiments are new.

Many promising applications for particle swarms require direct human control, but user interfaces to thousands---or millions---of particles is a daunting human-swarm interaction (HSI) challenge. Our early work with over a hundred hardware robots and thousands of simulated particles demonstrated that direct human control of large swarms is possible, \cite{Becker2013b}. 
Unfortunately, the logistical challenges of repeated experiments with over one hundred robots prevented large-scale tests. 
There is currently no comprehensive understanding of user interfaces for controlling multi-robot systems with massive populations.  
This paper presents a tool for investigating HSI methods through statistically significant numbers of experiments.

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{MainExpFig.pdf}\end{overpic}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} 
A swarm of particles, all controlled by a uniform control input, can be effectively controlled by a hybrid controller that knows only the mean and variance of the robot distribution.  
Here a swarm of particles (kilobot robots) pushes a green hexagon toward the goal (see video attachment).
}
\end{figure}
